---
title: "Homework 5"
author: "Teshawna Badu"
date: 11/20/2021
output: github_document
---

I'm an R Markdown document!

```{r setup}
library(tidyverse)
library(dplyr)
library(janitor)
library(readr)
library(readxl)
```

## Question 1 
The problem involves using data gathered and made public by _The Washington Post_ on homicides in 50 large U.S cities.

```{r}
homicide_df = 
  read_csv("./homicide-data.csv", na = c("","Unknown")) %>% 
  mutate(city_state = str_c(city, state),
         resolution = case_when(
           disposition == "Closed without arrest" ~ "unsolved",
           disposition == "Open/No arrest" ~ "unsolved",
           disposition == "Closed by arrest" ~ "solved" 
         )) %>%
  relocate(city_state) %>%
  filter(city_state != "TulsaAL")
```
The raw data is has 52,179 rows of data, with 12 variables. 

For city Baltimore, MD
```{r}
baltimore_df = homicide_df %>%
  filter(city_state == "BaltimoreMD")
baltimore_summary = 
  baltimore_df %>%
  summarize(unsolved = sum(resolution == "unsolved"),
            n = n())
baltimore_test = 
  prop.test(x = baltimore_summary %>% pull(unsolved),
            n = baltimore_summary %>% pull(n))
baltimore_test %>%
  broom::tidy()
```

Run prop.test for each of the cities in the dataset
```{r}
prop_test_function = function(city_df) {
  
  city_summary = 
  city_df %>%
  summarize(unsolved = sum(resolution == "unsolved"),
            n = n())
  city_test = 
    prop.test(x = city_summary %>% pull(unsolved),
              n = city_summary %>% pull(n))
  return(city_test)
  
}
homicide_df %>%
  filter(city_state == "AlbuquerqueNM") %>%
  prop_test_function()
```

```{r}
results_df = 
  homicide_df %>%
  nest(data = uid:resolution) %>%
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>%
  select(city_state, tidy_results) %>%
  unnest(tidy_results) %>%
  select(city_state, estimate, starts_with("conf"))
results_df
```

create a plot showing estimates and confidence intervals
```{r}
results_df %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
  
```

```{r}
homicide_df %>%
  group_by(city_state) %>%
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  ) %>%
  mutate(
    test_results = map2(unsolved, n, prop.test),
    tidy_results = map(test_results, broom::tidy)
  ) %>%
  select(city_state, tidy_results) %>%
  unnest(tidy_results) %>%
  select(city_state, estimate, starts_with("conf"))
```

## Question 2
Create and clean dataframe 
```{r, warning=FALSE, message=FALSE}
files_df <- tibble(
  files = list.files("./data")) %>%
  mutate(files = str_c("data", files, sep = "/"))
research_df <- files_df %>%
  mutate(respondents = map(files, read_csv)) %>%
  mutate(study_arm = case_when(str_detect(files, "exp") ~ "Experiment",
                               str_detect(files, "con") ~ "Control"),
         participant_number = as.factor(parse_number(files))) %>%
  unnest(respondents) %>%
  pivot_longer(cols = week_1:week_8, names_to = "week", values_to = "observations") %>%
  mutate(week = as.numeric(parse_number(week)))
```

Create spaghetti graph of observations over time split by study arm
```{r, warning=FALSE, message=FALSE}
research_df %>%
  ggplot(aes(x = week, y = observations, color = participant_number)) +
  geom_line() +
  ylab("Observations") +
  xlab("Weeks") +
  facet_grid(cols = vars(study_arm)) +
  ggtitle("Observations for each arm over Time ")
```

For the spaghetti plot, we see that participants in the control arm report similar observations over time. In contrast, participants in the experimental arm report different observations over time.


## Question 3
```{r}
set.seed(10)
iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

Writing function & Testing 
```{r}
iris_missing_function = function(x) {
  if (is_numeric(x)) {
    mean_nonmissing = round(mean(x, na.rm = TRUE, 1))
    x = replace_na(x, mean_nonmissing)}
  else if (is.character(x)) {
    x = replace_na(x, "virginica")}
  return(x)
}
iris_fillin = 
  map_df(iris_with_missing, iris_missing_function) %>% 
  as.tibble()
knitr::kable(iris_fillin)
view(iris_fillin)
```

